Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA

### 2021-06-30 paper/tex/sections/results.tex
reduce detectable properties grid to 6 panels
Updates from Overleaf

\begin{figure*}[tp]
    \centering
    \includegraphics[width=\textwidth]{2_dcos_on_sc.png}
    \caption{Density distribution of detectable BHBH, BHNS and NSNS binaries are shown together with the LISA sensitivity curve. In the top panel we show all systems with the LISA verification binaries over plotted (star symbols, \citealp{Kupfer+2018}). In the bottom panels we separate by type. Contours show the percentage of the population enclosed. The remaining 2\% of the population is shown as dots with a size that scales with the sampling weight. For reference we show lines where a circular binary of average mass $\avg{\mathcal{M}_c}$ would reside for a given remaining inspiral time (vertical lines) and distance (diagonal line). To highlight the role of eccentricity we further show the signal expected for an eccentric binary at 30 kpc. The coloured line in the bottom panels shows a contour that encloses 90\% of the population that is circular. See Sec.~\ref{sec:dcos_on_sc} for a discussion.}
    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve, where each panel corresponds to \textbf{top:} combined density plot for all DCO types (BHBH, BHNS and NSNS) \textbf{bottom:} three panels with individual density distribution of different DCO types. In each panel, we plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries). If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights. The inset colourbars indicate the percentage of the population represented by each contour and the annotated mass is the average chirp mass for all binaries in the panel, which is used in plotting the grid lines. We plot diagonal lines of constant distance, where the straight lines show the signal for a circular binary of average chirp mass, whilst the curved line shows the signal for an eccentric binary with $e = 0.98$. The vertical lines indicate the inspiral time for a circular binary with the average chirp mass. In the top panel we overlay the LISA verification binaries from \citet{Kupfer+2018}. In the bottom panels we add the 90\% contour line for only the circular sources to show how the distribution changes without eccentric sources present.}
    \label{fig:dcos_on_sc}
\end{figure*}

@@

\subsection{Distributions for the fiducial model}\label{sec:fiducial_distributions}

@@

\subsubsection{Black Hole Mass}
For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $88\%$ and $90\%$ respectively below $11 \unit{M_{\odot}}$. This is because, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation. The mass distribution extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes. Indeed we expect $35\%$ and $39\%$ of detected BHBH and BHNS systems to contain a black hole in the lower mass gap. Therefore, LISA could help to confirm or rule out the existence of the lower mass gap.

>>>>

\begin{figure*}[tp]
    \centering
    \includegraphics[width=\textwidth]{2_dcos_on_sc.png}
    \caption{Density distribution of detectable BHBH, BHNS and NSNS binaries are shown together with the LISA sensitivity curve. In the top panel we show all systems with the LISA verification binaries over plotted (star symbols, \citealp{Kupfer+2018}). In the bottom panels we separate by type. Contours show the percentage of the population enclosed. The remaining 2\% of the population is shown as dots with a size that scales with the sampling weight. For reference we show lines where a circular binary of average mass $\avg{\mathcal{M}_c}$ would reside for a given remaining inspiral time (vertical lines) and distance (diagonal line). To highlight the role of eccentricity we further show the signal expected for an eccentric binary at 30 kpc. The coloured line in the bottom panels shows a contour that encloses 90\% of the population that is circular. See Sec.~\ref{sec:dcos_on_sc} for a discussion.}
    \label{fig:dcos_on_sc}
\end{figure*}

@@

\subsection{Properties of the detectable systems}\label{sec:fiducial_distributions}

@@

\subsubsection{Black Hole Mass}
For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $88\%$ and $90\%$ respectively below $11 \unit{M_{\odot}}$. Unlike ground-based detector, LISA is not biased to higher masses and so the mass distribution more closely follows the IMF. In addition, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation, resulting the less massive black holes. The mass distribution extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes. Indeed we expect $35\%$ and $39\%$ of detected BHBH and BHNS systems to contain a black hole in the lower mass gap. Therefore, LISA could help to confirm or rule out the existence of the lower mass gap.
